Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-05-30 latex/afm-cs-main.tex
Update to latest results, with xy-feedforward.

\begin{figure}
  \includesvg[width=1\columnwidth]{figures/cs_raster_images_4-26-2019}
  \caption{Raster and compressed sensing images of a 5 micron square area of the
    CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
    indicated by the red line are shown in Fig.~\ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure}

\begin{table}[t!]
  \centering
  \caption{Performance metrics for the scans taken on 4-26-2019. All CS images
    filtered with TV denoising, $\mu$=100.}
  \begin{tabular}{cccccc}
    \input{tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
  \end{tabular}
  \label{tab:rast_vs_cs_v1}
\end{table}

@@

\begin{figure*}[t!]
  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_3-20-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are included.}
  \label{fig:pixel_rows}
\end{figure*}

@@

>>>>

\begin{figure*}
  \includesvg[width=1\textwidth]{figures/cs_raster_images_4-26-2019}
  \caption{Raster and compressed sensing images of a 5 micron square area of the
    CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
    indicated by the red line are shown in Fig.~\ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}

\begin{table}[t!]
  \centering
  \caption{Performance metrics for raster and CS scans.}
  \begin{tabular}{cccccc}
    \input{tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
  \end{tabular}
  \label{tab:rast_vs_cs_v1}
\end{table}

@@

\begin{figure*}[t!]
  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_4-26-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are included.}
  \label{fig:pixel_rows}
\end{figure*}

@@

\subsection{Comparison to sub-line sampling}
Compressed sensing so far does not look good if we compare to subline sampling. The left panel of Fig.~\ref{fig:subline} shows a 5~Hz raster scan taken with 128 lines which takes approximately 25 seconds. We use that data to produce a 128 by 512 pixel image, and then use basic linear interpolation to fill produce a 512 by 512 pixel image. The CS image with the nearest acquisition time (15\% at 4~Hz) is shown in the right panel. The raster scan looks better and has basically the same RDI, and better SSIM and PSNR numbers. We conclude there is no reason to use CS.
\begin{figure}
  \includesvg[width=1\columnwidth]{figures/subline_vs_cs.svg}
  \caption{(left) A 128 line raster scan interpolated onto 512 lines. (left) the CS scan with the nearest time.}
  \label{fig:subline}
\end{figure}
